API design for machine learning software: experiences from the scikit-learn project

### 2013-06-24 paper.tex
Fix latex comment broken by text wrapping and add missing 'and'
move 1.0 release mention to the end

\section{Future Work}
A \sklearn~1.0 release is nearing,
but several problems must still be resolved.
At present, the library does not support some classical machine learning tasks,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Topics like structured prediction or reinforcement learning are
considered off-topic for the project, since they would require quite different
data representations and APIs.

@@

>>>>

\section{Future Work}
There are several problems with the current scikit-learn interface which
will be resolved in the future.
At present, the library does not support some classical machine learning tasks,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Topics like structured prediction or reinforcement learning are
considered off-topic for the project, since they would require quite different
data representations and APIs.

@@

These API issues will be addressed in the future in preparation for
the 1.0 release of scikit-learn.
